Using Incremental Many-to-One Queries to Build a Fast and Tight Heuristic for A* in Road Networks

### 2021-10-19 paper/ch_potentials.tex
add alternative results

In~\cite{adgw-arrn-13} Abraham et al. describe a variation of the penalty method to directly obtain alternative routes rather than an alternative graph:
Just return the first path which shares less than 80\% with the original path and has stretch less than $1+\epsilon$.
However, their approach uses a simpler penalization schema.
We also implement this variant with CH-Potentials but stick to the penalization schema from Kobitzsch~\cite{kobitzsch2015alternative}.
This leads to some qualitative improvements compared to the results reported in~\cite{adgw-arrn-13}.

@@

>>>>

In~\cite{adgw-arrn-13} Abraham et al. describe a variation of the penalty method to directly obtain alternative routes rather than an alternative graph:
Just return the first path which shares less than 80\% with the original path and has stretch less than $1+\epsilon$.
However, their approach uses a simpler penalization schema.
We also implement this variant with CH-Potentials but stick to the penalization schema from Kobitzsch~\cite{kobitzsch2015alternative} and denote this approach as \emph{penalty routes}.
This leads to some qualitative improvements compared to the results reported in~\cite{adgw-arrn-13}.

@@

\subsubsection{Alternative Routes}

Our implementation of the penalty method reproduces the qualitative results reported in~\cite{kobitzsch2015alternative} (for random queries on DIMACs Europe we on average achieve a total distance of 2.93, an average distance of 1.04, 5.57 decision edges and a success rate of 98.7\% with 6.7 iterations).
The average running times to compute an alternative graph are 1.37\,s on DIMACs Europe and 0.85\,s on OSM Germany.
These running times are roughly one order of magnitude slower than the results achieved by Kobitzsch.
The simpler penalty routes approach is much faster and takes only 156\,ms on DIMACs Europe and 66\,ms on OSM Germany.
This is two orders of magnitude faster than the running times reported in~\cite{adgw-arrn-13} which is not surprising since their implementation uses an unaccelerated Dijkstra.
Due to the advanced penalization schema, our average qualitative results differ from~\cite{adgw-arrn-13}: the success rate is with 96.8\% slightly higher, the UBS with around 9\% slightly worse, the sharing is with 42\% somewhat higher but the local optimality, which was the weakest point in the original approach, with 21\% significantly better.
Finding these alternatives takes only 1.44 iterations on average.
This makes CH-Potential-based penalty routes a simple and feasible practical approach to compute alternative routes.
